### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Article Documentation Complete

\subsection{Sprint 5: Finalise Article}

>>>>

\subsection{Sprint 5: Finalise Article}
The final phase of developing the article involved formatting it in an academic journal style as well as completing the remaining sections from Sprint 4. 
\\\\
From the literature study and review of the case studies, various theories were selected to be used within the synthesis section. These included Merrill's First Principles, the ARCS model of motivation, the knowledge domain explanations and a framework for teaching preschool children. These were selected on the basis that they provided comprehensive information regarding effective teaching methods which would be combined with the information from the case studies - that being the design principles and philosophies. 
\\\\
Any and all correlations between these theories and design principles were mapped out and consolidated to produce the several qualities a serious game needs to be effective in an educational context. Some principles applied to a certain rule were also applied to others as well when it was deemed to be a helpful factor for the specific quality. The results of this are discussed in the following chapter - Chapter \ref{Chapter4}.
\\\\ 
The final aspect of development of this article was to format it in an academic journal style. For this, the PDF creation software \LaTeX was used along with an IEEE template document.
